RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
typo fix
didn't we already cover dc:title?

and can ask for a particular element using the standard list subsetting
mechanism (i.e. either the name of an element or it's numeric position),

@@

Following the link we can see that `dc` refers to the "Dublin Core"
vocabulary, and the term `title` refers to the title of a creative work
(as opposed to the title of a person, a legal title, the verb title, etc).
Such explicit definitions allow a computer to reason about these objects,
as we shall see later.

>>>>

and can ask for a particular element using the standard list subsetting
mechanism (i.e. either the name of an element or its numeric position),

@@

<!-- I feel like we already covered what dc:title is -->
Following the link we can see that `dc` refers to the "Dublin Core"
vocabulary, and the term `title` refers to the title of a creative work
(as opposed to the title of a person, a legal title, the verb title, etc).
Such explicit definitions allow a computer to reason about these objects,
as we shall see later.
